---
title: "Growth Curves and gamlss()"
author: "Ian Handel"
date: "31/10/2017"
output: 
  github_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(gamlss)
library(gamlss.nl)

set.seed(113)
```

## Simulate some growth curves

Rate mean for simulation: `r (rate_mean <- 0.01)`

Assym mean for simulation: `r (assym_mean <- 37)`

```{r}
N <- 200

dat <- tibble(id = 1:N,
              rates = rnorm(N, rate_mean, 0.001),
              assym = rnorm(N, assym_mean, 5)) %>% 
  inner_join(as_tibble(expand.grid(id = 1:N,
                                   days = seq(5, 1000, 5))),
             by = "id") %>% 
  mutate(weight = assym * (1 - exp(-days * rates)) + rnorm(nrow(.), 0, 1)) %>% 
  sample_frac(0.05)
```




## Plot them
```{r}

ggplot(dat, aes(x = days, y = weight, group = id)) +
  geom_line(alpha = 0.3)
```

## Now fit model
```{r, warning=FALSE}
mod <- nlgamlss(y = weight,
                mu.formula = ~ A * (1 - exp(- days * B)),
                sigma.formula = ~ 1,
                data = dat,
                family = NO,
                mu.fix = FALSE,
                sigma.fix = FALSE,
                mu.start = c(100, 0.1),
                sigma.start = 10)

summary(mod)
```

